\begin{thebibliography}{9}
\bibitem{redesProfundas} S. O. Arik \& M. Chrzanowski \& A. Coates \& G. Diamos \& A. Gibiansky \& Y. Kang \& X. Li \& J. Miller \& J. Raiman \& S. Sengupta \& M. Shoeybi. Deep Voice: Real-time neural text-to-speech. International Conference on Machine Learning, 2017.
\bibitem{redesProfundas2} Sotelo, Jose \& Mehri, Soroush \& Kumar, Kundan \& Santos, Joao Felipe \& Kastner, Kyle \& Courville, Aaron \& Bengio, Yoshua, ``Char2wav: End-to-end speech synthesis''. International Conference on Learning Representations, 2017.
\bibitem{prosodiaYEntonacion} Yamagishi, Junichi \& Onishi, Koji \& Masuko, Takashi \& Kobayashi, Takao. (2005). Acoustic Modeling of Speaking Styles and Emotional Expressions in HMM-Based Speech Synthesis. IEICE Transactions on Information and Systems. E88D. 10.1093/ietisy/e88-d.3.502. 
\bibitem{prosodiaYEntonacion2} Nose, Takashi \& Yamagishi, Junichi \& Masuko, Takashi \& Kobayashi, Takao. (2007). A Style Control Technique for HMM-Based Expressive Speech Synthesis. IEICE Transactions. 90-D. 1406-1413. 10.1093/ietisy/e90-d.9.1406. 
\bibitem{praat} Boersma, Paul (2001). Praat, a system for doing phonetics by computer. Glot International 5:9/10, 341-345.
\bibitem{hts} Pagina de descarga de HTS, 6 de febrero 2019, http://hts.sp.nitech.ac.jp/?Download
\bibitem{secytMujer} Torres, Humberto M., \& Jorge A. Gurlekian. ``Automatic determination of phrase breaks for Argentine Spanish.'' Speech Prosody 2004, International Conference. 2004.
\bibitem{loc1pal} Torres, Humberto M. \& Jorge A. Gurlekian \& C. C. Mercado. "Aromo: Argentine spanish TTS system." Proc. VII Jornadas en Tecnología del Habla and III Iberian SLTech Workshop, IberSPEECH.
\bibitem{cmuArtic} Kominek, John \& W Black, Alan. (2004). The CMU Arctic speech databases. SSW5-2004.
\bibitem{statisticalParam} Zen, H. \& Braunschweiler, N. \& Buchholz, S. \& Gales, M. J. \& Knill, K.  \& Krstulovic, S. \& Latorre, J. (2012). Statistical parametric speech synthesis based on speaker and language factorization. IEEE transactions on audio, speech, and language processing, 20(6), 1713-1724.
\bibitem{phoneticAndProsodic} Yoshimura, Takayoshi. ``Simultaneous modeling of phonetic and prosodic parameters, and characteristic conversion for HMM-based text-to-speech systems.'' Nagoya Institute of Technology, Japan (2002).
\bibitem{speakerAdaptativeTrainingLink} Demo del modelo CMU-ARCTIC-ADAPT,  http://hts.sp.nitech.ac.jp/archives/2.3/HTS-demo\_CMU-ARCTIC-ADAPT.tar.bz2
\bibitem{speakerSim} Wester, M., \& Karhila, R. (2011, May). Speaker similarity evaluation of foreign-accented speech synthesis using HMM-based speaker adaptation. In Acoustics, Speech and Signal Processing (ICASSP), 2011 IEEE International Conference on (pp. 5372-5375). IEEE.
\bibitem{phoneticCapturing} Prahallad, K. \& Black, A. W. \& Mosur, R. (2006, May). Sub-phonetic modeling for capturing pronunciation variations for conversational speech synthesis. In Acoustics, Speech and Signal Processing, 2006. ICASSP 2006 Proceedings. 2006 IEEE International Conference on (Vol. 1, pp. I-I). IEEE.
% como funciona el ehmm alignment
\bibitem{spanishInfluencedEnglish}  Goldstein, B. (2001). Transcription of Spanish and Spanish-influenced English. Communication Disorders Quarterly, 23(1), 54-60.
\bibitem{SpekerInterpolationRef} Yoshimura, T. \& Masuko, T. \& Tokuda, K. \& Kobayashi, T. \& Kitamura, T. (1997). Speaker interpolation in HMM-based speech synthesis system. In Fifth European Conference on Speech Communication and Technology.
\bibitem{festivalDownload} Pagina de descarga de Festival $2.4$, 6 de febrero 2019, http://www.cstr.ed.ac.uk/downloads/festival/2.4/
\bibitem{festvoxDownload} Pagina de descarga de Festvox, 6 de febrero 2019, http://festvox.org/download.html
\bibitem{speechToolDownload} The Edinburgh Speech Tools Library, 6 de febrero 2019, http://www.cstr.ed.ac.uk/projects/speech\_tools
\end{thebibliography}
